---
title: "Code RMarkdown"
author: "Robson Cruz"
date: "30/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

We’ve spent a lot of time getting R and RStudio working, learning about projects and version control - you are practically an expert at this! There is one last major functionality of R/RStudio that we would be remiss to not include in your introduction to R - [Markdown!]

## What is R Markdown?
R Markdown is a way of creating fully reproducible documents, in which both text and code can be combined. In fact, these lessons are written using R Markdown! That’s how we make things:

    bullets
    **bold**
    *italics*
    [links](links)
    or run inline r code

nd by the end of this lesson, you should be able to do each of those things too, and more!

Despite these documents all starting as plain text, you can render them into HTML pages, or PDFs, or Word documents, or slides! The symbols you use to signal, for example, bold or italics is compatible with all of those formats.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
